Causal graph analysis of COVID-19 observational data in German districts reveals effects of determining factors on reported case numbers

### 2021-04-19 manuscript/v6_medrxiv_revision_2/discussion.Rmd
add paragraphic social determinants

>>>>

A recent review on COVID-19 based on evidence from the US and UK concludes that low socioeconomic status groups are being hit harder by the pandemic [@Wachtler2020Socioeconomic]. Albeit specific pathways remain unclear, many studies found associations with poverty or its correlates such as poor and potentially overcrowded housing conditions. For Germany, a higher case fatality of COVID-19 cases in districts with higher socioeconomic deprivation has also been reported just recently, which was especially pronounced in the second wave of the pandemic [@rki2021sozialeunterschiede].
